The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-21 design.tex
add nomecalture

\subsubsection{Assumptions, nomenclature} % (fold)
\label{ssub:assumptions_nomenclature}
job
order
task
service-call
abstract machine
resource
service
demander
provider
platform
rank
hardness

@@

\subsection{Operation mode} % (fold)
\label{sub:operation_mode}

@@

\subsection{Interactions and decisions} % (fold)
\label{sub:interactions_and_decisions}

\subsection{Controlling rules} % (fold)
\label{sub:controlling_rules}

% subsection controlling_rules (end)

>>>>

\subsubsection{Assumptions, nomenclature} % (fold)
\label{ssub:assumptions_nomenclature}

\begin{table}[!h]
  \begin{framed}
    \nomenclature{$A$}{radius of}
    \nomenclature{$B$}{position of}
    \nomenclature{$C$}{further nomenclature}
    \printnomenclature
  \end{framed}
\end{table}

job
order
task
service-call
abstract machine
resource
service
demander
provider
platform
rank
hardness

@@

\subsection{Interactions and decisions} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Demander}
\label{subs:Demander}
For Task

\subsubsection{Provider}
\label{subs:Provider}
For Resource

For Service-call

For Service

\subsection{Operation mode} % (fold)
\label{sub:operation_mode}
Outsource

@@

\subsection{Controlling rules} % (fold)
\label{sub:controlling_rules}
Platform control the provider
% subsection controlling_rules (end)
